Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-05 documentation/paper.tex
Added some ICN information to paper

The essence of this algorithm, then, is a positive feedback loop in which, by using the network's most confident predictions in the training process, the desired (simpler) function is reinforced, when a conventional supervised learning system would have learned the more complex function that is taught by the ground truths.

@@

RESULTS PENDING

@@

RESULTS PENDING

>>>>

The essence of these 2 algorithms, then, is a positive feedback loop in which, by using the network's most confident predictions in the training process, the desired (simpler) function is reinforced, when a conventional supervised learning system would have learned the more complex function that is taught by the ground truths.

Performance of the supervised learning systems was quantified by how accurately they reproduced the labels provided to them (on a validation set). They were observed to learn to separate the calibration runs from background runs, including the percentage of alpha particles present in the calibration runs. One of the main intents of semi-supervised learning is to address the impure training data. Therefore, their performance is quantified by how well it is able to replicate Acoustic Parameter, rather than simply reproduce the labels provided.

@@

@@

During a grid search of these parameters (in addition to regularization parameters of the network), the best accuracy achieved for replication of Acoustic Parameter was exactly 100\%. The mean of all epochs within that training run was 98\%. Further demonstrating this is a powerful algorithm and that high performance was not a one-off, 35\% of the training runs replicated Acoustic Parameter with a mean accuracy greater than 92\%.
